Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks

### 2023-04-24 paper.tex
chore: on MARL

\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{cleveref}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
%
\usepackage{listings}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

@@

The remainder of this paper is structured as follows. First we introduce the relevant background and problem formulation in \Cref{sec:background}. Afterwards we introduce our approach in Section~\ref{sec:approach}. Section~\ref{sec:eval} outlines the performed experiments and discusses the obtained results. Finally, we will present our conclusions in Section~\ref{sec:conclusion}.

@@

\section{Field-informed Reinforcement Learning}
\label{sec:approach}
\ga{Page budget: 2/3 pages \\}
\ga{Plan: we should discuss the approach in detail, including the system model, the learning dynamics.
Particularly, I would like to highlight how the each node in the graph is a local controller,
but it could be see as a global evolution, therefore we can use global information to inform the local controller.}
\subsection{System model}
\ga{Plan: 
  discussion about typical AC evalaution model, specifying how GNN (with 1-hop information diffusion)
  can be easily integrate with this distributed model
}
\subsection{Learning dynamics}
\ga{
  Plan: discuss about the choosing approach, that is Centralised Training and Distributed Execution.
  Particularly, we use DQN in which the neural network is a GNN. So, the dataset consist in a set of graphs,
  where each graph is a snapshot of the system. 
  The target is the Q-value of the action taken in the current state.
  Explain how this can be then use for distributed controller.
}
\section{Evaluation}
\label{sec:eval}
\ga{Page budget: 2 pages \\}
\ga{Plan: we should discuss the robot aggregation scenario, specifiying the state space, the action space, the reward function.
I dunno if it makes sense to discuss the variants (i.e., fixed area, two ares and moving area). We will see.
}
\subsection{Scenario}

>>>>

\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{cleveref}
\usepackage{acronym}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
%
\usepackage{listings}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

\acrodef{DecPOMDP}[DecPOMDP]{decentralized partially observable Markov decision processes}

@@

The remainder of this paper is structured as follows. First we introduce the relevant background and problem formulation in \Cref{sec:background}. Afterwards we introduce our approach in Section~\Cref{sec:approach}. Section~\Cref{sec:eval} outlines the performed experiments and discusses the obtained results. Finally, we will present our conclusions in Section~\Cref{sec:conclusion}.

@@

Reinforcement learning (RL) has gained a lot of interest recently, 
 thanks to its successful application in various scenarios, 
 ranging from video games (such as Alpha Go and Atari) 
 to chatbots (like ChatGPT). 
% 
In RL, an agent (i.e., a smart entity capable of making decisions) 
 performs actions in an environment (i.e., everything outside the agent) according to a policy, 
 with the goal of maximizing long-term rewards.

One interesting application of RL is when there are multiple learning agents involved. 
 Such scenarios are referred to as multi-agent reinforcement learning (MARL). 
 While standard RL approaches use Markov decision processes to model the world, 
 in MARL for distributed systems, the notion of 
 \acp{DecPOMDP} is used.

A \ac{DecPOMDP} represents a sequential game, 
 in which each agent receives a local observation about the world they 
 inhabit and receives a joint immediate reward in response to the actions they take. 
% 
\ga{Improve, if necessary, the following paragraph.}
Formally, a DecPOMDP is defined as a tuple $<N, S, \{A_i\}, P, R, \{\Omega_i\}, O, \gamma>$, 
 where $N$ is the total number of agents that live in the environment, 
 $S$ is the state set of the environment, 
 $\{A_i\}$ is the set of actions for agent $i$ and $A$ is the joint action space, 
 $P$ is the probability transition function, 
 $R$ is the immediate joint reward function, and 
 $\{\Omega_i\}$ is the set observation function for the agent $i$,
 $O$ is the observation space, and finally $\gamma$ is the discount factor.
%
On top of this model, each agent try to learn a policy $\pi_i$ in order 
 to maximise the long term join reward signal.

In base of some of this concept, 
 we have several different MARL, like cooperative MARL (i.e., the reward function incetivize collective outcomes)
 heterogenous MARL (i.e., the agents have different action space and policy) and
 homogenous MARL (i.e., the agents have the same action space and policy).
%  
In particular, in this work we consider homogenous many agent RL, 
 where, N >> 2 and action space of each agent and the policy is the same (i.e., the agents are interchangeable)
\section{Field-informed Reinforcement Learning}
\label{sec:approach}
\ga{Page budget: 2/3 pages \\}
\ga{Plan: we should discuss the approach in detail, including the system model, the learning dynamics.
Particularly, I would like to highlight how the each node in the graph is a local controller,
but it could be see as a global evolution, therefore we can use global information to inform the local controller.}
\subsection{System model}
\ga{Plan: 
  discussion about typical AC evalaution model, specifying how GNN (with 1-hop information diffusion)
  can be easily integrate with this distributed model
}
\subsection{Learning dynamics}
\ga{
  Plan: discuss about the choosing approach, that is Centralised Training and Distributed Execution.
  Particularly, we use DQN in which the neural network is a GNN. So, the dataset consist in a set of graphs,
  where each graph is a snapshot of the system. 
  The target is the Q-value of the action taken in the current state.
  Explain how this can be then use for distributed controller.
}
\section{Evaluation}
\label{sec:eval}
\ga{Page budget: 2 pages \\}
\ga{Plan: we should discuss the robot aggregation scenario, specifiying the state space, the action space, the reward function.
I dunno if it makes sense to discuss the variants (i.e., fixed area, two ares and moving area). We will see.
}
\subsection{Scenario}
